---
title: "R Notebook"
output: html_notebook
---

Install and Load RMySQL 
-----------------------

```{r}
#install.packages("RMySQL")
library(RMySQL)
```

Connecting to MySQL:
--------------------
Once the RMySQL library is installed create a database connection object.

```{r}
mydb = dbConnect(MySQL(), user='stressdbuser', 
                 password='#October218', 
                 dbname='stressdb', 
                 host='35.194.173.89')
```

Listing Tables and Fields:
--------------------------
Now that a connection has been made we list the tables and fields in the database we connected to.

```{r}
dbListTables(mydb)
```

This will return a list of the tables in our connection. 

```{r}
dbListFields(mydb, 'screen')
```

This will return a list of the fields in some_table.

Running Queries:
----------------
Queries can be run using the dbSendQuery function.
dbSendQuery(mydb, 'drop table if exists some_table, some_other_table')

- Making tables:
We can create tables in the database using R dataframes.

dbWriteTable(mydb, name='table_name', value=data.frame.name)

Retrieving data from MySQL:
-----------------------------
To retrieve data from the database we need to save a results set object.

```{r}
rs = dbSendQuery(mydb, "select * from screen")
screendata = fetch(rs, n=-1)
screendata<-transform(screendata, screen_status=as.factor(screen_status))
head(screendata, 10)
```

Plot Chart
----------

```{r}
plot(screendata$screen_status)
```