---
title: "Workshop 5 Solution"
author: "Veerasak Kritsanapraphan"
date: ''
output: pdf_document
---

For the first two problems we'll use the Cars93 data set from the MASS library.

```{r}
library(MASS)
```

#### 1. Manipulating data frames

Use the `transform()` and `log()` functions to create a new data frame called `Cars93.log` that has `MPG.highway` and `MPG.city` replaced with `log(MPG.highway)` and `log(MPG.city)`.

```{r}
Cars93.log <- transform(Cars93, MPG.highway = log(MPG.highway), MPG.city = log(MPG.city)) 
```

#### 2. Functions, lists, and if-else practice

**(a)** Write a function called `isPassingGrade` whose input `x` is a number, and which returns `FALSE` if `x` is lower than 50 and `TRUE` otherwise.

```{r}
isPassingGrade <- function(x) {
  did.pass <- TRUE
  if(x < 50) {
    did.pass <- FALSE
  }
  did.pass
}

isPassingGrade(45)
isPassingGrade(90)

# Here's an alternative, using different syntax

isPassingGrade2 <- function(x) (x >= 50)

isPassingGrade2(45)
isPassingGrade2(90)
```

**(b)** Write a function called `sendMessage` whose input `x` is a number, and which prints `Congratulations` if `isPassingGrade(x)` is `TRUE` and prints `Oh no!` if `isPassingGrade(x)` is `FALSE`.

```{r}
sendMessage <- function(x) {
  if(isPassingGrade(x)) {
    print("Congratulations!")
  } else {
    print("Oh no!")
  }
}

sendMessage(45)
sendMessage(90)

# Here's another way of accomplishing the same thing

sendMessage2 <- function(x) print(ifelse(isPassingGrade(x), "Congratulations", "Oh no!"))

sendMessage2(45)
sendMessage2(90)
```
