---
title: "Workshop 7"
author: "Veerasak Kritsanapraphan"
date: ""
output: html_document
---

We'll begin by loading all the required packages.
```{r}
library(MASS)
library(lattice)
library(ggplot2)
```

#### Plotting the Cars93 data

This problem uses the Cars93 dataset from the MASS package.

**(a)** Use `qplot` to create a scatterplot with Price on the y-axis and EngineSize on the `x-axis`.  

```{r, fig.align='center', fig.height=4, fig.width=5}
qplot(x = EngineSize, y = Price, data = Cars93)
```

**(b)** Repeat part (a) using the `ggplot` function and `geom_point()` layer.

```{r, fig.align='center', fig.height=4, fig.width=5}
ggplot(Cars93, aes(x = EngineSize, y = Price)) + geom_point()
```

**(c)** Repeat part (b), but this time specifying that the `color` mapping should depend on `Type` and the `shape` mapping should depend on `DriveTrain`.  

```{r, fig.align='center', fig.height=4, fig.width=5}
ggplot(Cars93, aes(x = EngineSize, y = Price, colour = Type, shape = DriveTrain)) + geom_point()
```

