---
title: "Lab 8 Solutions"
author: "Veerasak Kritsanapraphan"
date: ""
output: 
  html_document:
    fig_width: 7
    fig_height: 5
---

We'll begin by loading some packages.
```{r}
library(MASS)
library(plyr)
library(ggplot2)
library(reshape)
```

Let's form our favourite birthwt data set.

```{r}
# Rename the columns to have more descriptive names
colnames(birthwt) <- c("birthwt.below.2500", "mother.age", "mother.weight", 
    "race", "mother.smokes", "previous.prem.labor", "hypertension", "uterine.irr", 
    "physician.visits", "birthwt.grams")

# Transform variables to factors with descriptive levels
birthwt <- transform(birthwt, 
            race = as.factor(mapvalues(race, c(1, 2, 3), 
                              c("white","black", "other"))),
            mother.smokes = as.factor(mapvalues(mother.smokes, 
                              c(0,1), c("no", "yes"))),
            hypertension = as.factor(mapvalues(hypertension, 
                              c(0,1), c("no", "yes"))),
            uterine.irr = as.factor(mapvalues(uterine.irr, 
                              c(0,1), c("no", "yes")))
            )
```

### ANOVA with birthwt data

**(a)** Create a new factor that categorizes the number of physician visits into three levels: 0, 1, 2, 3 or more.  

```{r}
phys.visit.binned <- birthwt$physician.visits
phys.visit.binned[phys.visit.binned >= 3] <- "3.or.more"
birthwt <- transform(birthwt, phys.visit.binned = as.factor(phys.visit.binned))

birthwt$phys.visit.binned
```

**Hint**: One way of doing this is with mapvalues, by mapping all instances of 3, 4,... etc, to "3 or more".

**(b)** Run an ANOVA to determine whether the average birth weight varies across number of physician visits.

```{r}
aov.birthwt <- aov(birthwt.grams ~ phys.visit.binned, data = birthwt)
summary(aov.birthwt)
```

The p-value is greater than 0.05, so the variation in birthweight across number of physician visits is not statistically significant.  

```{r}
plot(aov.birthwt)
```

```{r}
posthoc <- TukeyHSD(x=aov.birthwt, 'phys.visit.binned', conf.level=0.95)
posthoc
plot(posthoc)
```