---
title: "Workshop 2 Solutions"
author: "Veerasak Kritsanapraphan"
date: ""
output: html_document
---

### 1. Changing the author field and file name.

##### (a) Change the `author:` field on the Rmd document from Your Name Here to your own name.

##### (b) Rename this file to "lab01_YourHameHere.Rmd", where YourNameHere is changed to your own name.

### 2.  Hello World!

Here's an R code chunk that prints the text 'Hello world!'.

```{r}
print("Hello world!")
```

#### (a) Modify the code chunk below to print your name
```{r}
print("Veerasak Kritsanapraphan")
```

<br>

### 3.  Creating sequences
We just learned about the `c()` operator, which forms a vector from its arguments.  If we're trying to build a vector containing a sequence of numbers, there are several useful functions at our disposal.  These are the colon operator `:` and the sequence function `seq()`.

##### `:` Colon operator: 
```{r}
1:10 # Numbers 1 to 10
127:132 # Numbers 127 to 132
```

##### `seq` function: `seq(from, to, by)`
```{r}
seq(1,10,1) # Numbers 1 to 10
seq(1,10,2) # Odd numbers from 1 to 10
seq(2,10,2) # Even numbers from 2 to 10
```

> To learn more about a function, type `?functionname` into your console.  E.g., `?seq` pulls up a Help file with the R documentation for the `seq` function.

#### (a) Use `:` to output the sequence of numbers from 3 to 12
```{r}
3:12
```

#### (b) Use `seq()` to output the sequence of numbers from 3 to 30 in increments of 3
```{r}
seq(3, 30, 3)
```

#### (c) Save the sequence from (a) as a variable `x`, and the sequence from (b) as a variable `y`.  Output their product `x*y`
```{r}
x <- 3:12
y <- seq(3, 30, 3)
x * y
```

<br>

### 4. Cars data

We'll look at data frame and plotting in much more detail in later classes.  For a previous of what's to come, here's a very basic example.

For this example we'll use a very simple dataset.  The `cars` data comes with the default installation of R.  To see the first few columns of the data, just type `head(cars)`.

```{r}
head(cars)
```

We'll do a bad thing here and use the `attach()` command, which will allow us to access the `speed` and `dist` columns of `cars` as though they were vectors in our workspace.

```{r}
attach(cars) # Using this command is poor style.  We will avoid it in the future.
speed
dist
```

#### (a) Calculate the average and standard deviation of speed and distance.
```{r}
mean(speed)
sd(speed)
mean(dist)
sd(dist)
```

<br>

<br>  We can easily produce a histogram of stopping distance using the `hist` function.
```{r}
hist(dist) # Histogram of stopping distance
```

The `plot(x,y,...)` function plots a vector `y` against a vector `x`.  You can type `?plot` into the Console to learn more about the basic plot function. 

#### (b) Use the `plot(x,y)` function to create a scatterplot of dist against speed.
```{r}
plot(speed, dist)
```