---
title: "Workshop 8 Solutions"
author: "Veerasak Kritsanapraphan"
date: ''
output:
  pdf_document: default
  html_document: default
---

We'll begin by loading all the packages we might need.
```{r}
library(MASS)
library(plyr)
library(reshape)  # You may need to install this one first!
library(ggplot2)
```

### Is the data normal?

**(a)** Construct histograms of `MPG.highway`, one plot for each `Origin` category.

```{r}
qplot(x = MPG.highway, data = Cars93, facets = ~Origin, geom = "histogram", fill = Origin, binwidth = 2)
```

**(b)** Does the data look to be normally distributed?

The histograms don't really look normally distributed, so we might be better off using the non-parametric test.

**(c)** Construct qqplots of `MPG.highway`, one plot for each `Origin` category.  Overlay a line on each plot using with `qqline()` function.

```{r, fig.height = 4}
par(mfrow = c(1,2))
# USA cars
with(Cars93, qqnorm(MPG.highway[Origin == "USA"]))
with(Cars93, qqline(MPG.highway, col = "blue"))
# Foreign cars
with(Cars93, qqnorm(MPG.highway[Origin == "non-USA"]))
with(Cars93, qqline(MPG.highway, col = "blue"))
```

**(d)** Does the data look to be normally distributed?

The non-USA MPG.highway data looks very far from normally distributed.


### Testing means between two groups

**(a)** Using the Cars93 data and the `t.test()` function, run a t-test to see if average `MPG.highway` is different between US and non-US vehicles.

Try doing this both using the formula style input and the `x`, `y` style input.

```{r}
# Formula version
mpg.t.test <- t.test(MPG.highway ~ Origin, data = Cars93)
mpg.t.test
```

```{r}
mpg.z.test <- z.test(x=Cars93$Origin, y = Cars93$MPG.highway, alternative = "two.sided", mu = 0, sigma.x = NULL,
  sigma.y = NULL, conf.level = 0.95)
mpg.z.test
```

# x, y version
with(Cars93, t.test(x = MPG.highway[Origin == "USA"], y = MPG.highway[Origin == "non-USA"]))
```

**(b)** What is the confidence interval for the difference?

```{r}
mpg.t.test$conf.int
```

**(c)** Repeat part (a) using the `wilcox.test()` function.

```{r}
mpg.wilcox.test <- wilcox.test(MPG.highway ~ Origin, data = Cars93)
mpg.wilcox.test
```

## What about one tail?

### Mean of X less then Y
####t.test(formula,alternative="less")

```{r}
with(Cars93, t.test(x = MPG.highway[Origin == "USA"], y = MPG.highway[Origin =="non-USA"], alternative="less")) 
```


### Mean of Y greater than X
####t.test(formula,alternative="greater")
```{r}
with(Cars93, t.test(x = MPG.highway[Origin == "USA"], y = MPG.highway[Origin =="non-USA"], alternative="greater")) 
```

